### 2014-05-30 ACL2014/experiments.tex
Updated latex files

\subsection{Data}
The public dataset that we demonstrate result on is adapted from the query logs of AOL (\aol dataset) search engine \cite{Pass06}. 
Moreover, we show results on large-scale query logs (billion queries) sampled from a commercial search engine. The \dataA  
denotes $1$\% sampled query logs from a commercial search engine, \dataB ($10$\%), and  \dataC ($100$\%). 
Each query point has an associated feature vector, that is high dimensional and sparse. 
Feature vector contains the  webpages (urls) that are weighted based on click through rate on the urls for the query term.  
As a pre-processing step, we remove all those queries that have less than or equal to five clicked urls. 
Table \ref{tab:data} summarizes the statistics of our several query-logs datasets. Our biggest dataset has $N=600$ million unique queries 
with billions of unique urls as features.

@@

\subsection{Evaluating Vanilla LSH} 
\label{subsec:eval:vanillaLSH}
In the first experiment, we vary $L=\{1,10,28,55\}$ with fixed $K=16$. 
$L$ denotes the number of tables and $K$ denotes the length of the index of the table. 
If we increase $K$ (increasing the precision to reduce false positives), we also need to 
increase $L$ to get good recall (increasing the recall to reduce false negatives). 
Table \ref{tab:varyL} shows that increasing $L$ leads to better recall, 
however at the expense of more comparisons. In addition, having large $L$ 
means generating large number of random projection bits that is 
both time and memory intensive. Hence, we fix $L=10$, 
which leads to reasonable recall with fewer comparisons.

In the second experiment, we vary $K=\{4,8,16\}$ with fixed $L=10$. 
As expected, Table \ref{tab:varyK} shows that increasing $K$ reduces the number of 
comparisons and worse recall. This is intuitive as we reduce the value of $K$, it leads to 
brute force linear search. Hence, we fix $K=16$ to have fewer number of comparisons.

In the third experiment, we fix $L=10$ and $K=16$ and increase the size of training data. 
Table \ref{tab:varyData} demonstrates that as we increase the training data size, 
the number of comparisons also increase. This result indicates that $K$ and $L$  
needs to be tuned with respect to a specific dataset. $K$ and $L$ can be tuned by 
randomly sampling small set of queries.\footnote{In this paper, we randomly select 2000 queries to tune $K$ and $L$ parameters.}

@@

\begin{table}
\centering
\begin{tabular}{|c|r|c|}
\hline
Data & Comparisons & Recall \\
\hline
\aol & 57  & .63 \\
\dataA  &  1,052 & .67 \\
\dataB    & 10,515 & .64 \\
\hline 
 \end{tabular}
\caption{\footnotesize{Fixed $K=16$  and $L=10$ on different sized datasets with $\tau=0.7$.}}
\label{tab:varyData}
\end{table}

@@

paraphrasing \cite{ganitkevitch13Paraphrase}

>>>>

\subsection{Data}
The public dataset that we demonstrate result on is adapted from the query logs of AOL (\aol dataset) search engine \cite{Pass06}. 
Moreover, we show results on large-scale query logs (hundreds of millions of queries) sampled from a commercial search engine. The \dataA  
denotes $1$\% sampled query logs from a commercial search engine, \dataB ($10$\%), and  \dataC ($100$\%). 
Each query point has an associated feature vector, that is high dimensional and sparse. 
Feature vector contains the  webpages (urls) that are weighted based on click through rate on the urls for the query term.  
As a pre-processing step, we remove all those queries that have less than or equal to five clicked urls. 
Table \ref{tab:data} summarizes the statistics of our several query-logs datasets. Our biggest dataset has $N=600$ million unique queries 
with billions of unique urls as features.

@@

\subsection{Evaluating Vanilla LSH} 
\label{subsec:eval:vanillaLSH}
In the first experiment, we vary $L=\{1,10,28,55\}$ with fixed $K=16$. 
$L$ denotes the number of hash tables and $K$ denotes the length of the index of the buckets in the table. 
If we increase $K$ (increasing the precision to reduce false positives), we also need to 
increase $L$ to get good recall (increasing the recall to reduce false negatives). 
Table \ref{tab:varyL} shows that increasing $L$ leads to better recall, 
however at the expense of more comparisons. In addition, having large $L$ 
means generating large number of random projection bits and hash tables that is 
both time and memory intensive. Hence, we fix $L=10$, 
which leads to reasonable recall with fewer comparisons.

In the second experiment, we vary $K=\{4,8,16\}$ with fixed $L=10$. 
As expected, Table \ref{tab:varyK} shows that increasing $K$ reduces the number of 
comparisons and worse recall. This is intuitive as  
the larger value of $K$ leads to larger 
gap between probabilites of collision between close queries 
and far queries (see Section \ref{sec:vlsh}). 
Hence, we fix $K=16$ to have fewer number of comparisons.

In the third experiment, we fix $L=10$ and $K=16$ and increase the size of training data. 
Table \ref{tab:varyData} demonstrates that as we increase the training data size, 
the number of comparisons also increase. This result indicates that $K$   
needs to be tuned with respect to a specific dataset, 
as large $K$ will reduce the probability of dis-similar 
queries falling within the same bucket. 
$K$ and $L$ can be tuned by 
randomly sampling small set of queries.\footnote{In this paper, we randomly select 2000 queries to tune parameter $K$.}

@@

\begin{table}
\centering
\begin{tabular}{|c|r|c|}
\hline
Data & Comparisons & Recall \\
\hline
\aol & 57  & .63 \\
\dataA  &  1,052 & .67 \\
\dataB    & 10,515 & .64 \\
\dataC    & - & - \\
\hline 
 \end{tabular}
\caption{\footnotesize{Fixed $K=16$  and $L=10$ on different sized datasets with $\tau=0.7$.}}
\label{tab:varyData}
\end{table}

@@

% paraphrasing \cite{ganitkevitch13Paraphrase}
% maybe include deduplication results
